\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-08-02 paper/sp.tex
thanks sven
small model issues

In addition, we assume that many entries in the $D$-vector will be zero
(the ``sparsity'' assumption).
In order to encourage this, we optimize not $\chi^2$ but a regularized objective function
\begin{eqnarray}
\hat{\theta} &\leftarrow& \argmin_{\theta}\left[\frac{1}{2}\,\chi^2(\theta) + ||\lambda\cdot\theta||_1^1\right]
\quad ,
\end{eqnarray}
where
$\lambda$ is a $D$-vector of regularization parameters (such that we can regularize
different parts of the $x_n$ vectors differently),
and $||x||_1^1$ is the L1-norm or sum of absolute values of the components of $x$.
This kind of regularization adds a convex term to the optimization and leads to
sparse optima.
We will set the value $\lambda$ of the $D$-vector of regularization strengths by a
very coarse cross-validation.

@@

For every star $n$ in the full Parent Sample we construct the feature
vector $x_n$ as
\begin{eqnarray}
x_n\T &\equiv& [1, G_n, {BP}_n, {RP}_n, J_n, H_n, K_n, W_{1n}, W_{2n}, f_{1n}, f_{2n}, \cdots, f_{Ln}]
\quad ,
\end{eqnarray}
where the 1 permits a linear offset,
the photometry is from \gaia, \zmass, and \wise, respectively,
and
the fluxes in the $L=7405$ \apogee\ spectral pixels (for which there are reliably
and consistently data) for star $n$ are denoted
$f_{1n}$, $f_{2n}$, and so on.
These feature vectors live in a $D$-dimensional space where $D=7414$
For every star $n$ in either of the Training Sets we additionally require---in
addition to these feature vectors---a \gaia-measured parallax $\gparallax_n$
and uncertainty $\sigma_n$.

@@

\acknowledgements
It is a pleasure to thank
  Coryn Bailer-Jones (\acronym{MPIA}),
  Andy L. Jones,
  Daniel Michalik (\acronym{ESTEC}),
  Melissa Ness (Columbia),
  and the participants in the \acronym{MPIA} Milky Way Group Meeting
for help with this project.
This project was developed in part at the
2018 \acronym{NYC} Gaia Sprint, hosted by the Center for Computational Astrophysics of
the Flatiron Institute in New York City in 2018 June.

>>>>

In addition, we assume that many entries in the $D$-vector will be zero
(the ``sparsity'' assumption).
In order to encourage this, we optimize not $\chi^2$ but a regularized objective function
\begin{eqnarray}
\hat{\theta} &\leftarrow& \argmin_{\theta}\left[\frac{1}{2}\,\chi^2(\theta) + ||\lambda\ast\theta||_1^1\right]
\quad ,
\end{eqnarray}
where
$\lambda$ is a $D$-vector of regularization parameters (such that we can regularize
different parts of the $x_n$ vectors differently),
the ``$a\ast b$'' operator indicates element-wise multiplication of vectors $a$ and $b$,
and $||y||_1^1$ is the L1-norm or sum of absolute values of the components of $y$.
This kind of regularization adds a convex term to the optimization and leads to
sparse optima.
We will set the value $\lambda$ of the $D$-vector of regularization strengths by a
very coarse cross-validation.

@@

For every star $n$ in the full Parent Sample we construct the feature
vector $x_n$ as
\begin{eqnarray}
x_n\T &\equiv& [1, G_n, {BP}_n, {RP}_n, J_n, H_n, K_n, W_{1n}, W_{2n}, \ln f_{1n}, \ln f_{2n}, \cdots, \ln f_{Ln}]
\quad ,
\end{eqnarray}
where the 1 permits a linear offset,
the photometry is from \gaia, \zmass, and \wise, respectively,
the fluxes in the $L=7405$ \apogee\ spectral pixels (for which there are reliably
and consistently data) for star $n$ are denoted
$f_{1n}$, $f_{2n}$, and so on,
and we have taken logarithms of those fluxes.
These feature vectors live in a $D$-dimensional space where $D=7414$
For every star $n$ in either of the Training Sets we additionally require---in
addition to these feature vectors---a \gaia-measured parallax $\gparallax_n$
and uncertainty $\sigma_n$.

@@

\acknowledgements
It is a pleasure to thank
  Coryn Bailer-Jones (\acronym{MPIA}),
  Sven Buder (\acronym{MPIA}),
  Andy L. Jones,
  Daniel Michalik (\acronym{ESTEC}),
  Melissa Ness (Columbia),
  and the participants in the \acronym{MPIA} Milky Way Group Meeting
for help with this project.
This project was developed in part at the
2018 \acronym{NYC} Gaia Sprint, hosted by the Center for Computational Astrophysics of
the Flatiron Institute in New York City in 2018 June.
